---
title: ""
---

</br></br>

### Chromebook Data Science is an online educational program created by a [team](./soon.html) the [Johns Hopkins Data Science Lab](http://jhudatascience.org/). Chromebook Data Science is a sequence of [courses](./soon.html) that assumes basic computer literacy as a pre-requisite and builds to performing basic data science skills. Our [philosophy](./soon.html) is to make data science a completely cloud based activity so people can work from where they are rather than being forced to move to high cost centers of data science. If you are a company looking for well-trained data scientists and want to support Chromebook Data Science consider becoming a [partner organization](./partners.html). 

-----

```{r,echo=FALSE,warning=FALSE}
source("helper2.R")
two_column("The problem","Routine and manual jobs are rapidly being automated using newly developed computer, robotic, and machine learning technologies. This trend will accelerate over time.","./img/01_index.png")
```

-----

```{r,echo=FALSE,warning=FALSE}
source("helper2.R")
two_column("A solution","At the same time there is strong and growing demand for people with skills in data processing, analysis, and reporting.","./img/02_index.png",iside="right")
```

-----

## ____

```{r,echo=FALSE,warning=FALSE}
source("helper2.R")
two_column("Challenges","But people who are currently unemployed or employed in manual or other low tech jobs face barriers to transitioning to data science jobs. The high cost of computing, education, and the centralization of jobs in high-cost metro areas prevent career transitions.","./img/04_index.png",iside="left")
```

------

<center> <h1> <strong> Our approach </strong> </h1> </center>

</br>

```{r,echo=FALSE,warning=FALSE}
source("helper2.R")
two_column("Minimize computer costs","We have developed a curriculum that is fully cloud based to allow students to do data science with cheap laptops like Chromebooks.","./img/chromebook.png",iside="right")
```

-----

```{r,echo=FALSE,warning=FALSE}
source("helper2.R")
two_column("Free courses","It is possible to complete our Chromebook Data Science program entirely online, for free. We couple will our online curriculum with in person tutoring and support to ensure equal access for individuals who have not been traditionally well served by online programs.","./img/08_index.png",iside="left",link="./curriculum.html", linktext="See our curriculum")
```

-----

```{r,echo=FALSE,warning=FALSE}
source("helper2.R")
two_column("Allow remote work","Data science work can be done from anywhere there is an Internet connection. Chromebook Data Science can be completed from anywhere. ","./img/remotework.png",iside="right")
```

-----

```{r,echo=FALSE,warning=FALSE}
source("helper2.R")
two_column("Faciliate Networking","We partner with companies who need to fill data science roles to place our graduates in remote data science jobs. If you are looking for data scientists consider becoming a Chromebook Data Science hiring partner. ","./img/remotework.png", link="./partners.html",linktext="Become a Hiring Partner")
```

