---
title: ""
---

</br></br>

## Chromebook Data Science (CBDS) is a free online educational [program](./cbds.html) to help anyone who can read, write, and use a computer to move into data science, the [number one rated job](https://www.glassdoor.com/List/Best-Jobs-in-America-LST_KQ0,20.htm). It is offered by faculty members in the Johns Hopkins Department of Biostatistics, Bloomberg School of Public Health.

-----

```{r,echo=FALSE,warning=FALSE}
source("helper2.R")
two_column("Why data science?","Data science is the number one rated job by Glassdoor and there are more than 350,000 new data science expected by 2020.","./img/why_data_science/dataanalysis.png")
```


-----

```{r,echo=FALSE,warning=FALSE}
source("helper2.R")
two_column("Our goal","Our goal is to help people find good-paying jobs. Our approach provides an opportunity to train for the jobs of the future, without spending money or having to move.","./img/index/04_index.png",iside="right")
```

------

<center> <h1> <strong> Our approach </strong> </h1> </center>

------

</br>

```{r,echo=FALSE,warning=FALSE}
source("helper2.R")
two_column("We minimize computer costs","We have developed an online program that lets students do data science using only a web browser and cheap computers like Chromebooks.","./img/index/chromebook.png",link="https://www.google.com/chromebook/",linktext="Learn more about Google Chromebook", iside="right")
```

-----

```{r,echo=FALSE,warning=FALSE}
source("helper2.R")
two_column("Free courses","Our CBDS program is entirely online and you can take it for free. You can take the classes any time and at your own pace. You get a certificate for each CBDS online class from Leanpub.","./img/index/08_index.png",iside="left",link="./curriculum.html", linktext="See our curriculum")
```


-----

```{r,echo=FALSE,warning=FALSE}
source("helper2.R")
two_column("Learn anywhere","Data science work can be done from anywhere there is an Internet connection. CBDS can be completed from anywhere. ","./img/index/remotework.png",iside="right")
```

-----

```{r,echo=FALSE,warning=FALSE}
source("helper2.R")
two_column("Finding jobs","Our program covers soft skills you need to get data science jobs, including how to network and get your name out there. We are also interested in working with partner companies who need to fill data science roles to place our graduates in remote and local data science jobs. (If you are looking for data scientists consider becoming a CBDS hiring partner). ","./img/index/networking.png")
```

<br> 

------

### More questions? Great! Check out the list of our [partners](./partners.html), [frequently asked questions](./faq.html), learn about our [team](./team.html) or [contact us](./contact.html).
